Something About Workflow Scheduling in Clouds

### 2011-12-26 paper/paper.tex
Add some notes for related work

\numberofauthors{2}
\author{
    \alignauthor Maciej Malawski and Jarek Nabrzyski\\
       \affaddr{University of Notre Dame}\\
       \affaddr{South Bend, IN, USA}\\
       \email{\{mmalawsk,naber\}@nd.edu}
    \alignauthor Gideon Juve and Ewa Deelman\\
       \affaddr{USC Information Sciences Institute}\\
       \affaddr{Marina del Rey, CA, USA}\\
       \email{\{gideon,deelman\}@isi.edu}
}

@@

\section{Introduction}
Here is a citation~\cite{Yu2005} just to make bibtex work.

\section{Related Work}

\section{Problem Description}

\section{Algorithms}

@@

\section{Conclusions}
Conclusions go here.

>>>>

\numberofauthors{2}
\author{
    \alignauthor Maciej Malawski and Jarek Nabrzyski\\
       \affaddr{University of Notre Dame}\\
       \affaddr{111 Information Technology Center}\\
       \affaddr{Notre Dame, IN, USA}\\
       \email{\{mmalawsk,naber\}@nd.edu}
    \alignauthor Gideon Juve and Ewa Deelman\\
       \affaddr{USC Information Sciences Institute}\\
       \affaddr{4676 Admiralty Way}\\
       \affaddr{Marina del Rey, CA, USA}\\
       \email{\{gideon,deelman\}@isi.edu}
}

@@

\section{Introduction}

\section{Related Work}
General policy and rule-based approaches to dynamic provisioning (e.g. Amazon Auto Scaling\footnote{http://aws.amazon.com/autoscaling} and RightScale\footnote{http://www.rightscale.com}).

Policy-based approaches for scientific workloads (e.g. \cite{Marshall2010})

Workflow scheduling in utility grids (e.g. \cite{Yu2005})

Workflow ensemble scheduling in clouds (e.g. \cite{Mao2011})

\section{Problem Description}
\subsection{Application Model}
\subsection{System Model}

\section{Algorithms}
\subsection{Dynamic Provisioning Dynamic Scheduling (DPDS)}
\subsection{Workflow-Aware DPDS (WA-DPDS)}
\subsection{Static Provisioning Static Scheduling (SPSS)}

@@

\section{Conclusion and Future Work}
